Dataset-level report

### 2019-11-13 analysis/reports/dat_report_template.Rmd
break bbs into two

dat <- readd(paste0("dat_s_dat_", this_dataset), cache = cache, character_only = T)
loadd(all_di, cache = cache)

>>>>

dat <- readd(paste0("dat_s_dat_", this_dataset), cache = cache, character_only = T)
if(this_dataset == "bbs") {
  loadd(all_di_FALSE, cache = cache)
  loadd(all_di_TRUE, cache = cache)
  all_di = bind_rows(all_di_FALSE, all_di_TRUE)
  rm(all_di_FALSE)
  rm(all_di_TRUE)

  } else {
    loadd(all_di, cache = cache)
  }
